### 2025-06-12 paper/intro.tex
Emphasize this.

As a result, we demonstrate an approach where the entire specification,
optimiser, AD and code generation are available to us within a proof assistant
of our choice. We can prove facts about all the stages of the pipeline and
easily adjust them to our liking. We also demonstrate that some components can
be left only partially verified, where the effort of verification is judged
disproportionate to the benefit. We argue that such a liberating approach is
feasible in practice, at least for the times of dialectic of correctness and
performance.

The contributions of this paper are as follows:
\begin{enumerate}
  \item a rank-polymorphic array theory and implementation of
        the CNN from~\cite{cnn-array} in Agda;
  \item an embedded DSL in Agda which supports AD (reverse mode);
  \item an extraction mechanism for generating Futhark code from the DSL; and
  \item an experimental evaluation of the generated codes.
\end{enumerate}

>>>>

As a result, we demonstrate an approach where the entire specification,
optimiser, AD and code generation are available to us within a proof assistant
of our choice. We can prove facts about all the stages of the pipeline and
easily adjust them to our liking. We also demonstrate that some components can
be left only partially verified, where the effort of verification is judged
disproportionate to the benefit. We argue that such a liberating approach is
feasible in practice, at least for the times of dialectic of correctness and
performance. The overall goals is to demonstrate how to formulate a
computationally intensive problem in a proof assistant, transform it with
verification of key safety properties, and then pass it on to the other system
that can run the algorithm efficiently.

The contributions of this paper are as follows:
\begin{enumerate}
  \item a rank-polymorphic array theory and implementation of
        the CNN from~\cite{cnn-array} in Agda;
  \item an embedded DSL in Agda which supports AD (reverse mode);
  \item an extraction mechanism for generating Futhark code from the DSL; and
  \item an experimental evaluation of the generated code.
\end{enumerate}
